Gravitational Lens Modelling of Flux Ratio Anomalous System B1555+375

### 2015-03-03 papers/B1555_EdgeOn/B1555_letter.tex
Change in Table 3
little change in Discussion

While future large-scale surveys, such as the LSST, \simona{are expected to deliver new large samples of gravitationally lensed quasar, in the near future the discovery of new systems using} narrow-line quasar emission \citep{N14} \simona{will provide new invaluable statistical perspective on current constraints based on flux ratio anomalies. 
In this paper, we explore the alternative idea that flux ratio anomalies are not related to the presence of substructure but originate in a more complex host galaxy mass distribution than initially considered. To this end we use new infra-red data from the Strong lensing at High Angular Resolution Program(SHARP). The main goal of the SHARP} project \simona{is to re-observe} known quadruple and Einstein ring lens systems at a much higher angular resolution by making use of the Keck adaptive optics (AO) telescope and large interferometric arrays \citep{SHARP12,V12} . In particular, to better understand the cause of flux ratio anomalies in strong lens systems \simona{we focus on the lens modelling of the lens system B1555+375 (included in both the observational and theoretical analysis of  \citet{Dalal2002} and \citet{Xu14}, respectively) by making use of} the new information obtained from the latest SHARP infrared imaging. \simona{The paper is organized as follows: the latest SHARP data is introduced in section 2; in section 3 we present the lens model while the results of this analysis and their implication are discussed in section 4.}
%However, only small number of flux ratio anomalous systems in \simona{the} radio are \simona{currently} avaliable. Besides waiting for future large-scale survey such as LSST to find thousands of more new lens galaxies, another approach \simona{is to} seek out more flux ratio anomalous systems \simona{using} narrow-line quasar emission \citep{N14}. 
%	With expected growth in the number of samples, several groups have developed the technique to estimate the properties of substructures from flux ratio anomalous systems. \citet{V09, H13} both analyze the strong lens imaging to detect substructures lie infront of Einstein ring. Their methods improve the detectable mass limit and also show that high spatial resolution imaging is essential for the substructure study. On the other hand, numerical simulations on structure formation do not reach the concise conclusion on flux ratio anomalous systems. The latest study on the cause of flux anomalies from \citet{Xu14} shows the low probability of the existence of substructures in their studied systems. 
%	The Strong lensing at High Angular Resolution Program(SHARP) is a project aims on known quadruple and Einstein ring lensing systems \citep{SHARP12}. We obtain high-resoltion images from Keck adaptive optics(AO) and Hubble Space Telescope(HST) observations. 
%To better understand the cause of flux ratio anomaly in strong lensing systems, we model B1555+375, one of the systems discussed in \citet{Xu14}, with the new information obtained from the latest SHARP infrared imaging. We present the latest SHARP data in part 2, lens model of B1555+375 in part 3, and discussion in part 4.

@@

%%table3
\begin{table}
\begin{center}
\caption{Flux Ratios of B1555+375 Components.\label{tbl-3}}
\begin{tabular}{lccccc}
\tableline\tableline
				&Radio &Infrared  &Model-predicted\\
\tableline
A/B			&$1.8$ &$3.5$ &$1.7$  \\ 
A/C 		&$2.0$ &$1.0$ &$2.2$  \\
A/D			&$13.0$ &$5.4$ &$8.0$  \\
\tableline
\end{tabular}
%% Any table notes must follow the \end{tabular} command.
\tablecomments{Radio observation data quoted from Table 2 in \citet{Marlow}. Flux ratio between the merging double is much higher in infrared than in radio, which is believed to be caused by strong dust extinction from the edge-on disk.}
\end{center}
\end{table}

@@

Discussions on substructure searching in strong lensing system are mostly done by multiple images of lensed quasar. Until now there are a dozen(?) flux anomalous lensed quasars, and the number must increase in the future surveys. In the ideal case(no extinction and micro lensing), flux ratio anomalies are brought by substructure perturbations with the assumption that lens galaxy has smooth gravitational potential. Numerical simulations have examined this idea with known lensed quasars. In \citet{Xu14}, they found that substructure cannot expalin for all of radio flux anomalous phenomena. Only 1 out of 6 lens systems can be reproduced the flux anomaly by adding subhalos on to the system. The rest of them are only few percent likely to have substructure origined flux anomaly, including our target B1555+375. They conclude B1555+375 with improper lens model. This result can be supported by SHARP K-band image, which an edge-on disk lies across between the radio merging double A \& B. A more complicated lens model (e.g. include an exponential disk) must be applied on B1555+375.

In part 3, we present new lens models of B1555+375 with a bulge and an edge-on disk. Our models better match to the radio image positions than in \citet{Marlow} and also explain the flux ratio anomaly between components A and B. In our modelling, substructure is not neccessary to presence and a  exponential disk with high ellipcity well explains the observed flux ratio anomaly. This indicates that in B1555+375, flux ratio anomaly is caused by structure of lens galaxy itself rather than substructure. Our discover brings out a reminder: not all of flux ratio anomalies in lensed quasar indicate the existence of substructure even without the problem of dust extinction and micro lensing from stars. A complex host galaxy mass distribution can dominate flux ratio anomalous phenomenon in strong lensed quasar. Thus, one must fully consider non-substructure effects before gathering any statistics or serious analysis. Otherwise, these ``false'' substructures that detected by flux anomalies can serverly biased the data analysis. For the case oringinated by real  substructures, mass distribution of host galaxy may also influence the estimated mass and other derived properties. We would like to draw attention on this non-substructure effect in flux anomalous lensed quasar. Not untill non-substructure effects in flux ratio anomalous systems been understood, statistics from  lensed quasars may contain large systematic bias.

Our result also shows that multi-wavelength image is helpful on exploring flux ratio anomalous systems. Although radio data provides reliable information for constraint and modelling, optical and near-infrared imaging provides useful information about mass distribution of host galaxy. In the previous paper of SHARP, \citet{SHARP12} show that high resolution IR imaging improves the lens modelling. The improvement is even more dramatic in B1555+375 while adding an edge-on disk can well explain flux ratio anomaly. Lack of knowledge on lens galaxy surely leads to an improper lens model sometimes. With the first system being analyzed and shown that an edge-on disk can cause flux ratio anomaly, our follow up will be explore other SHARP systems. In Figure 3, all of these systems have a recognizable edge-on disk in infrared imaging. The flux ratio anomalies of these systems may also able to be explained by an edge-on disk structure.\\

>>>>

While future large-scale surveys, such as the LSST, \simona{are expected to deliver new large samples of gravitationally lensed quasar, in the near future the discovery of new systems using} narrow-line quasar emission \citep{N14} \simona{will provide new invaluable statistical perspective on current constraints based on flux ratio anomalies. 
In this paper, we explore the alternative idea that flux ratio anomalies are not related to the presence of substructure but originate in a more complex lens galaxy mass distribution than initially considered. To this end we use new infra-red data from the Strong lensing at High Angular Resolution Program(SHARP). The main goal of the SHARP} project \simona{is to re-observe} known quadruple and Einstein ring lens systems at a much higher angular resolution by making use of the Keck adaptive optics (AO) telescope and large interferometric arrays \citep{SHARP12,V12} . In particular, to better understand the cause of flux ratio anomalies in strong lens systems \simona{we focus on the lens modelling of the lens system B1555+375 (included in both the observational and theoretical analysis of  \citet{Dalal2002} and \citet{Xu14}, respectively) by making use of} the new information obtained from the latest SHARP infrared imaging. \simona{The paper is organized as follows: the latest SHARP data is introduced in section 2; in section 3 we present the lens model while the results of this analysis and their implication are discussed in section 4.}
%However, only small number of flux ratio anomalous systems in \simona{the} radio are \simona{currently} avaliable. Besides waiting for future large-scale survey such as LSST to find thousands of more new lens galaxies, another approach \simona{is to} seek out more flux ratio anomalous systems \simona{using} narrow-line quasar emission \citep{N14}. 
%	With expected growth in the number of samples, several groups have developed the technique to estimate the properties of substructures from flux ratio anomalous systems. \citet{V09, H13} both analyze the strong lens imaging to detect substructures lie infront of Einstein ring. Their methods improve the detectable mass limit and also show that high spatial resolution imaging is essential for the substructure study. On the other hand, numerical simulations on structure formation do not reach the concise conclusion on flux ratio anomalous systems. The latest study on the cause of flux anomalies from \citet{Xu14} shows the low probability of the existence of substructures in their studied systems. 
%	The Strong lensing at High Angular Resolution Program(SHARP) is a project aims on known quadruple and Einstein ring lensing systems \citep{SHARP12}. We obtain high-resoltion images from Keck adaptive optics(AO) and Hubble Space Telescope(HST) observations. 
%To better understand the cause of flux ratio anomaly in strong lensing systems, we model B1555+375, one of the systems discussed in \citet{Xu14}, with the new information obtained from the latest SHARP infrared imaging. We present the latest SHARP data in part 2, lens model of B1555+375 in part 3, and discussion in part 4.

@@

%%table3
\begin{table}
\begin{center}
\caption{Flux Ratios of B1555+375 Components.\label{tbl-3}}
\begin{tabular}{lccccc}
\tableline\tableline
				&5 GHz & 15 GHz & Ks  &Model-predicted\\
\tableline
A/B			&$1.8$ & $1.8$ & $3.5$ &$1.7$  \\ 
A/C 		&$2.0$ 	&$2.4$ &$1.0$ &$2.2$  \\
A/D			&$13.0$ &$ 12.9$ & $5.4$ &$8.0$  \\
\tableline
\end{tabular}
%% Any table notes must follow the \end{tabular} command.
\tablecomments{Radio observation data quoted from Table 2 and Table 3 in \citet{Marlow}. Flux ratio between the merging double is much higher in infrared than in radio, which is believed to be caused by strong dust extinction from the edge-on disk.}
\end{center}
\end{table}

@@

Discussions on substructure searching in strong lensing system are mostly done by multiple images of lensed quasar. In the ideal case (no extinction and micro lensing), flux ratio anomalies are brought by substructure perturbations with the assumption that lens galaxy has smooth gravitational potential. Numerical simulations have examined this idea with known lensed quasars. In \citet{Xu14}, they found that substructure cannot expalin for all of radio flux anomalous phenomena. Only 1 out of 6 lens systems can be reproduced the flux anomaly by adding subhalos on to the system. The rest of them are only few percent likely to have substructure origined flux anomaly, including our target B1555+375. They conclude B1555+375 with improper lens model. This result can be supported by SHARP K-band image, which an edge-on disk lies across between the radio merging double A \& B. A more complex lens model (e.g. include an exponential disk) must be applied on B1555+375.

In part 3, we present new lens models of B1555+375 with a bulge and an edge-on disk. Our models better match to the radio image positions than in \citet{Marlow} and also explain the flux ratio anomaly between components A and B. In our modelling, substructure is not neccessary to presence and a  exponential disk with high ellipcity well explains the observed flux ratio anomaly. This indicates that in B1555+375, flux ratio anomaly is caused by structure of lens galaxy itself rather than substructure. Although the number of radio loud flux anomalous lensed quasars remains small, new technique using narrow-line emission will enlarge the sample and bring statistical perspective on substructures in the near future. Our discover brings out a reminder: not all of flux ratio anomalies in lensed quasar indicate the existence of substructure even without the problem of dust extinction and micro lensing from stars. A complex lens galaxy mass distribution can dominate flux ratio anomalous phenomenon in strong lensed quasar. Thus, one must fully consider non-substructure effects before gathering any statistics or serious analysis. Otherwise, these ``false'' substructures that detected by flux anomalies can serverly biased the data analysis. For the case oringinated by real  substructures, mass distribution of lens galaxy may also influence the estimated mass and other derived properties. We would like to draw attention on this non-substructure effect in flux anomalous lensed quasar. [here for a precise estimate on substurcture number, mass function, property missing satellite problem]Not untill non-substructure effects in flux ratio anomalous systems been understood, statistics from lensed quasars may contain large systematic bias.

Our result also shows that multi-wavelength image is helpful on exploring flux anomalous quasars. Although radio data provides reliable information for constraint and modelling, optical and near-infrared imaging provides useful information about mass distribution of lens galaxy. In the previous paper of SHARP, \citet{SHARP12} show that high resolution IR imaging improves the lens modelling. The improvement is even more dramatic in B1555+375 while adding an edge-on disk can well explain flux ratio anomaly. Lack of knowledge on lens galaxy surely leads to an improper lens model sometimes. [Cant determine on substructure detection] With the first system being analyzed and shown that an edge-on disk can cause flux ratio anomaly, our follow up will be explore other SHARP systems. In Figure 3, all of these systems have a recognizable edge-on disk in infrared imaging. The flux ratio anomalies of these systems may also able to be explained by an edge-on disk structure.\\
